---
title: "Stabilization through pairwise PSF experiments"
author: "AS LSC"
date: "January 24th, 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = FALSE)
rm(list=ls())
```

# Main Text

We run models to estimate average survival-adjusted growth coefficients from 
interaction-only models using a zero-inflated gamma model

The interaction coefficient is calculated from above coefficients using the log-form 
of the bever 2003 equation for I_s, as used in Crawford et al 2019

```{r}

### packages
library(tidyverse)
library(nlme)
library(lme4)
library(lmerTest)
library(lmeresampler)
library(broom.mixed)
library(sjPlot)
library(glmmTMB)
library(tictoc)
library(broom.mixed)
library(patchwork)
library(performance)
library(AICcmodavg)
library(patchwork)
library(ggsignif)
library(jtools)

fpsf <- read_csv(file = "data/fpsf_final.csv")

spsf <- read_csv(file = "data/spsf_final.csv")

# Pair PSF models (ZIF-gamma)

m_pair.shade <- glmmTMB(data = spsf,
                   formula = Biomass.fin_orig ~ -1 + Height.ini_sc + Seedling.sp:Neighbour.sp + (1|SoilSource_TreeID),
                   family = ziGamma(link = "log"),ziformula = ~.)

m_pair.field <- glmmTMB(data = fpsf,
                   formula = Biomass.fin_orig ~ -1 + Height.ini_sc + Seedling.sp:Neighbour.sp + (1|TreeID),
                   family = ziGamma(link = "log"),ziformula = ~.,se = T)

models_a2 <- list(m_pair.shade,m_pair.field)
names(models_a2) <- c("spsf_pair","fpsf_pair")
save(models_a2,file = "results/model_objects.rdata")

```

### Computing Is and Is's CIs from models

```{r echo=T,message=F,include=TRUE,warning=FALSE}

load("results/model_objects.rdata")
splist0 <- c("ST","DZ","HI","BC","SC")

# function to calculate interaction coefficients for all pairs of species in an 
# experiment when model coefficients are supplied to it
iscalc <- function(biomass_co,logodds_co) 
{
  biomass_coef <- biomass_co
  logodds_coef <- logodds_co
  alpha <- exp(biomass_coef) * (1 - (exp(logodds_coef) / (1 + exp(logodds_coef))))
  # exp(biomass) because biomass/growth coefficient is on the log-scale;
  # exp(coeff) / (1 + exp(coeff) gives mortality probability
  # 1- above gives survival probability
  
  amat <- 
    alpha %>% 
    log() %>% #re dudenhoffer 2022 and Crawford 2019
    as_tibble(rownames = "pred") %>% 
    filter(pred != "Height.ini_sc") %>% 
    separate(col = "pred",
             into = c("seed","soil"),
             sep = ":") %>%
    mutate(soil_source = substr(soil,nchar(soil)-1,nchar(soil)),
           seed_source = substr(seed,nchar(seed)-1,nchar(seed))) %>% 
    select(-seed,-soil) %>% 
  pivot_wider(names_from = soil_source,
              values_from = value) %>% 
    column_to_rownames("seed_source")
  
  is <- 
    tibble(ispair = combn(x = splist0,m = 2) %>% t() %>% 
             as_tibble() %>% 
             mutate(ispair = paste0(V1,"_",V2)) %>% 
             pull(ispair),
               isval = NA_real_) %>% 
    column_to_rownames("ispair")

  is["ST_DZ","isval"] <- amat["ST","ST"] - amat["ST","DZ"] + amat["DZ","DZ"] - amat["DZ","ST"]
  is["ST_HI","isval"]  <- amat["ST","ST"] - amat["ST","HI"] + amat["HI","HI"] - amat["HI","ST"]
  is["ST_BC","isval"] <- amat["ST","ST"] - amat["ST","BC"] + amat["BC","BC"] - amat["BC","ST"]
  is["DZ_HI","isval"]  <- amat["DZ","DZ"] - amat["DZ","HI"] + amat["HI","HI"] - amat["HI","DZ"]
  is["DZ_BC","isval"] <- amat["DZ","DZ"] - amat["DZ","BC"] + amat["BC","BC"] - amat["BC","DZ"]
  is["HI_BC","isval"]  <- amat["HI","HI"] - amat["HI","BC"] + amat["BC","BC"] - amat["BC","HI"]
  
  if(ncol(amat) == 5) # shade house has 5 species, 1 extra species compared to field
  { 
    is["ST_SC","isval"] <- amat["SC","SC"] - amat["SC","ST"] + amat["ST","ST"] - amat["ST","SC"]
    is["DZ_SC","isval"]  <- amat["SC","SC"] - amat["SC","DZ"] + amat["DZ","DZ"] - amat["DZ","SC"]
    is["HI_SC","isval"] <- amat["SC","SC"] - amat["SC","HI"] + amat["HI","HI"] - amat["HI","SC"]
    is["BC_SC","isval"]  <- amat["SC","SC"] - amat["SC","BC"] + amat["BC","BC"] - amat["BC","SC"]
  }
return(is)
}

# Calculating mean Is values ####
is_shade <- 
  iscalc(biomass_co = fixef(models_a2$spsf_pair)$cond, # conditional coefficient - gamma distribution 
         logodds_co = fixef(models_a2$spsf_pair)$zi) %>%  # zero-inflated componenet
  rownames_to_column("pair")

is_field <- 
  iscalc(biomass_co = fixef(models_a2$fpsf_pair)$cond,
         logodds_co = fixef(models_a2$fpsf_pair)$zi) %>% 
  filter(!is.na(isval)) %>% # for SC species, not included in the field study
  rownames_to_column("pair")


# Calculating CIs around Is values through bootstrapping ####

nsims <- 9999

# myfunc extracts coefficients from the model input
myfunc <- function(x) { return(c(fixef(x)[[1]],fixef(x)[[2]]))}
 
tic()
 shade_boot <- 
   lme4::bootMer(x = models_a2[[1]],
                 FUN = myfunc,
                 nsim = nsims,
                 type = "parametric",
                 .progress = "win")
toc()
# save(shade_boot,file = "results/shade_boot.RData")

tic() 
 field_boot <- 
   lme4::bootMer(x = models_a2[[2]],
                 FUN = myfunc,
                 nsim = nsims,
                 type = "parametric",
                 .progress = "txt")
 
# save(field_boot,file = "results/field_boot.RData")
toc()

load("results/shade_boot.RData")
load("results/field_boot.RData")

 isci <- vector("list",2)
 names(isci) <- c("shade","field")
 isci[[1]] <- isci[[2]] <- vector("list",length = nsims)
 names(isci$shade) <- names(isci$field)
 
 for(i in 1:nsims) # takes a lot of time for n=9999
 {   
   isci$shade[[i]] <- iscalc(biomass_co = shade_boot$t[i,1:26],
                               logodds_co = shade_boot$t[i,27:52]) #5x5+1
 
   isci$field[[i]] <- iscalc(biomass_co = field_boot$t[i,1:17],
                             logodds_co = field_boot$t[i,18:34]) #4x4+1
     if(i %%100 == 0) {
       cat(paste0("currently on",i,"\n"))
       }
 }

 isci_s <- bind_cols(isci$shade) # ~ 5 mins
 names(isci_s) <- paste0("iter",
                         str_pad(string = c(1:nsims),width = 4,side = "left",pad = 0))
 isci_f <- bind_cols(isci$field) # ~ 5 mins
 names(isci_f) <- paste0("iter",
                         str_pad(string = c(1:nsims),width = 4,side = "left",pad = 0))

 # save(isci_s,file = "results/isci_s.RData")
 # save(isci_f,file = "results/isci_f.RData")

#####

load("results/isci_s.RData")
load("results/isci_f.RData")

# removing infinite values and plotting coefficients to check for outliers
isci_shade <- t(isci_s) %>% apply(.,MARGIN = 2,FUN = function(xx) ifelse(is.infinite(xx),NA_real_,xx)) %>% as_tibble()
isci_field <- t(isci_f) %>% apply(.,MARGIN = 2,FUN = function(xx) ifelse(is.infinite(xx),NA_real_,xx)) %>% as_tibble() %>%
  select(-ST_SC,-DZ_SC,-HI_SC,-BC_SC) 

# visualize coefficient spread
 par(mfrow = c(2,5))
 apply(X = isci_shade,MARGIN = 2,FUN = hist)
 par(mfrow = c(2,3))
 apply(X = isci_field,MARGIN = 2,FUN = hist)

 # see values of coefficient spread
field_coefsummary <- apply(X = isci_field,MARGIN = 2,FUN = summary) # bias correction is not needed
shade_coefsummary <- apply(X = isci_shade,MARGIN = 2,FUN = summary) # removing outliers manually on seeing the columns:
# e.g. sort(isci_shade$ST_DZ,decreasing = T)[1:100]
# which(isci_shade$ST_DZ>2) # 2 entries
# which(isci_shade$DZ_BC>2) # 2 entries
# which(isci_shade$HI_SC>2.9) # 2 entries
# which(isci_shade$DZ_SC>3.5) # 4 entries
isci_shade$ST_DZ[which(isci_shade$ST_DZ>2)] <- NA_real_ 
isci_shade$DZ_BC[which(isci_shade$DZ_BC>2)] <- NA_real_ 
isci_shade$HI_SC[which(isci_shade$HI_SC>2.9)] <- NA_real_ 
isci_shade$DZ_SC[which(isci_shade$DZ_SC>3.5)] <- NA_real_ 

isboth <- bind_rows(
  
  is_shade %>%  
    mutate(is_lci = apply(X = isci_shade,MARGIN = 2, FUN = function(x) quantile(x,probs = 0.025,na.rm = T)),
           is_uci = apply(X = isci_shade,MARGIN = 2, FUN = function(x) quantile(x,probs = 0.975,na.rm = T)),
           # is_se = apply(X = isci_shade, MARGIN = 2, function(xx) sd(xx,na.rm=T)),
           # lower_2se = isval - 2*is_se,lower_1se = isval - 1*is_se,
           # upper_2se = isval + 2*is_se,upper_1se = isval + 1*is_se,
           # pval = ifelse(lower_2se<0 & upper_2se < 0, "**",ifelse(lower_2se > 0 & upper_2se > 0, "**","ns")),
           mycopair = ifelse(pair %in% c("ST_DZ","ST_SC","DZ_SC"),yes = "conmycorrhizal",
                             no = ifelse(pair == "HI_BC","conmycorrhizal","heteromycorrhizal")),
           dataset = "shadehouse",
           pair = factor(pair,levels = c("ST_DZ","ST_SC","DZ_SC","HI_BC","ST_HI","ST_BC","DZ_HI","DZ_BC","HI_SC","BC_SC"))),
  
  is_field %>% 
  mutate(is_lci = apply(X = isci_field,MARGIN = 2, FUN = function(x) quantile(x,probs = 0.025,na.rm = T)),
         is_uci = apply(X = isci_field,MARGIN = 2, FUN = function(x) quantile(x,probs = 0.975,na.rm = T)),
         # is_se = apply(X = isci_field, MARGIN = 2, function(xx) sd(xx,na.rm=T)),
         # lower_2se = isval - 2*is_se,lower_1se = isval - 1*is_se,
         # upper_2se = isval + 2*is_se,upper_1se = isval + 1*is_se,
         # pval = ifelse(lower_2se<0 & upper_2se < 0, "**",ifelse(lower_2se > 0 & upper_2se > 0, "**","ns")),
         mycopair = ifelse(pair %in% c("ST_DZ","ST_SC","DZ_SC"),yes = "conmycorrhizal",
                           no = ifelse(pair == "HI_BC","conmycorrhizal","heteromycorrhizal")),
         dataset = "field",
        pair = factor(pair,levels = c("ST_DZ","HI_BC","ST_HI","ST_BC","DZ_HI","DZ_BC")))) %>% 
  mutate(dataset = factor(dataset,levels=c("shadehouse","field")))

write_csv(x = isboth,file = "results/isboth.csv")

```

### Figure 2 and 3

```{r echo=T,message=F,include=TRUE,warning=FALSE}
rm(list=ls())

isboth <- 
  read_csv(file = "results/isboth.csv") %>% 
  mutate(pair = 
           factor(pair,
                  levels = c("ST_DZ","ST_SC","DZ_SC","HI_BC", # conmyco
                             "ST_HI","ST_BC","DZ_HI","DZ_BC","HI_SC","BC_SC")), # heteromyco
         dataset = ifelse(dataset=="shadehouse","shade house",dataset),
         dataset = factor(dataset,
                  levels = c("shade house","field")))
  

# Figure 2 #### 

fig2 <- 
  ggplot(data = isboth,
         aes(y = isval,x = pair)) + 
  geom_hline(yintercept = 0,linetype = 2) +
  geom_col(aes(fill = mycopair),colour="black",linewidth=0.5) + 
  scale_fill_manual(name="",values = c("steelblue1","tomato4")) + 
  geom_errorbar(aes(ymin = is_lci, ymax = is_uci),
                linewidth =0.5,width=0.15) + 
  facet_grid(.~dataset,scales = "free_x",space = "free_x",drop = T) + 
  theme_classic() + 
  xlab("Species pairs") + ylab(expression("Interaction Coefficient, I"[s])) + 
  ggtitle("") +
  theme(legend.position = "top",
        panel.border = element_rect(colour = "black", fill=NA, linewidth=1),
        axis.text.x = element_text(angle = 45,vjust = 0.5))

ggsave(plot = fig2, # tiff would be nice but too big for github!
       filename = "results/fig2.png",device = "png",
       width = 8.3, height = 7, units = "in",dpi=600)

# Figure 3 #####

dat_fig3 <- isboth[,c("pair","isval","dataset")] %>% 
  mutate(dataset = factor(dataset,levels = rev(c("shade house","field"))))

fig3 <- 
  ggplot(data = dat_fig3,
                mapping = aes(y=dataset,x=isval)) + 
  
  geom_point(data = dat_fig3 %>% 
                   group_by(dataset) %>% summarize(mu = mean(isval)),
               mapping = aes(y=dataset,x=mu),
             colour="black",fill="grey50",stroke=1, size=4,shape=21) + 
    
  geom_jitter(alpha=0.7,size=3,height = 0.1,shape=1) + 
    theme_bw() + ylab("") + xlab("Interaction coefficient") + xlim(-2,2) + 
  geom_signif(comparisons = list(c("shade house","field")),
                test = "wilcox.test",
              test.args = list(alternative="two.sided",paired=F),
              map_signif_level = function(p) sprintf("p = %.2g", p),
              textsize = 3, y_position = c(1.5))
                
ggsave(plot = fig3,
       filename = "results/fig3.png",
       device = "png",width = 4, height = 1.5, units = "in",dpi=600)
```

# Supplementary Information

### Table A1: Model comparison with AIC (and R^2 - marginal only) to identify the predictor of initial size

```{r}
rm(list = ls())

spsf <- read_csv(file = "data/spsf_final.csv")
fpsf <- read_csv(file = "data/fpsf_final.csv")

# Biomass.fin ~ Biomass.ini + ...

maic_spsf <- list(
  glmmTMB(data = spsf,
              formula = Biomass.fin_orig ~ -1 + Height.ini_sc + Seedling.sp:Neighbour.sp + (1|SoilSource_TreeID),
              family = ziGamma(link = "log"),ziformula = ~.),
  glmmTMB(data = spsf,
              formula = Biomass.fin_orig ~ -1 + Leaves.ini_sc + Seedling.sp:Neighbour.sp + (1|SoilSource_TreeID),
              family = ziGamma(link = "log"),ziformula = ~.),
  glmmTMB(data = spsf %>% mutate(Biomass.ini_sc = scale(Biomass.ini)),
              formula = Biomass.fin_orig ~ -1 + Biomass.ini_sc + Seedling.sp:Neighbour.sp + (1|SoilSource_TreeID),
              family = ziGamma(link = "log"),ziformula = ~.))

maic_fpsf <- list(
  glmmTMB(data = fpsf,
              formula = Biomass.fin_orig ~ -1 + Height.ini_sc + Seedling.sp:Neighbour.sp + (1|TreeID),
              family = ziGamma(link = "log"),ziformula = ~.),
  glmmTMB(data = fpsf,
              formula = Biomass.fin_orig ~ -1 + Leaves.ini_sc + Seedling.sp:Neighbour.sp + (1|TreeID),
              family = ziGamma(link = "log"),ziformula = ~.),
  glmmTMB(data = fpsf %>% mutate(Biomass.ini_sc = scale(Biomass.ini)),
              formula = Biomass.fin_orig ~ -1 + Biomass.ini_sc + Seedling.sp:Neighbour.sp + (1|TreeID),
              family = ziGamma(link = "log"),ziformula = ~.))

mnames <- 
  expand.grid(c("Height","Leaves","Biomass"),c("spsf","fpsf")) %>% 
  mutate(mname = paste0(Var2,"_",Var1)) %>% 
  pull(mname)

r2 <- c(
  lapply(maic_spsf,FUN = function(x) r2_nakagawa(x,tolerance = 0)$R2_marginal),
  lapply(maic_fpsf,FUN = function(x) r2_nakagawa(x,tolerance = 0)$R2_marginal))

names(r2) <- mnames
  
# REML=F just in this supplement because REML=T can't be used for AIC comparison, apparently

tableS1 <- 
  bind_rows(
aictab(cand.set = maic_spsf,modnames = mnames[1:3]) %>% as_tibble() %>% 
  rename(resp=Modnames) %>% mutate(r2=unlist(r2[1:3]),model="s"),
aictab(cand.set = maic_fpsf,modnames = mnames[4:6]) %>% as_tibble() %>% 
  rename(resp=Modnames) %>% mutate(r2=unlist(r2[4:6]),model="f"))

write_csv(x = tableS1 %>% 
            separate(col=resp,
                     into = c("study","predictor"),
                     sep="_",remove=T) %>% 
            select(-LL,-Cum.Wt,-r2,-ModelLik),
          file = "results/tableA1_AIC_initsize.csv")
# using Height in the main model because it has the lowest AIC
```

### Figure A1: Individual PSFs from the zero-inflated model

```{r echo=T,message=F,include=TRUE,warning=FALSE}

rm(list = ls())
nsims = 9999

load("results/model_objects.rdata")
load("results/field_boot.RData")
load("results/shade_boot.RData")

adatcalc <- function(biomass_co,logodds_co) 
{
  biomass_coef <- biomass_co
  logodds_coef <- logodds_co
  alpha <- exp(biomass_coef) * (1 - (exp(logodds_coef) / (1 + exp(logodds_coef))))
  # exp(biomass) because biomass/growth coefficient is on the log-scale;
  # exp(coeff) / (1 + exp(coeff) gives mortality probability
  # 1- above gives survival probability
  
  adat <- 
    alpha %>% 
    # log() %>% #re dudenhoffer 2022 and Crawford 2019
    # ^ not needed to show individual PSFs on observed scale
    as_tibble(rownames = "pred") %>% 
    filter(pred != "Height.ini_sc") %>% 
    separate(col = "pred",
             into = c("seed","soil"),
             sep = ":") %>%
    mutate(soil_source = substr(soil,nchar(soil)-1,nchar(soil)),
           seed_source = substr(seed,nchar(seed)-1,nchar(seed))) %>% 
    select(-seed,-soil) %>% 
    rename(alpha = value)
  
  return(adat)
}

# mean model coefficients - computing survival-adjusted biomass estimates
indpsf_shade <- 
  adatcalc(biomass_co = fixef(models_a2$spsf_pair)$cond, # conditional coefficient - gamma distribution 
         logodds_co = fixef(models_a2$spsf_pair)$zi)  # zero-inflated component
indpsf_field <- 
  adatcalc(biomass_co = fixef(models_a2$fpsf_pair)$cond,
         logodds_co = fixef(models_a2$fpsf_pair)$zi)

# CIs of coefficients computing survival-adjusted biomass for each bootstrap
indpsf_field_nsims <- indpsf_shade_nsims <- vector(mode = "list",length = nsims)
names(indpsf_field_nsims) <- names(indpsf_shade_nsims) <- 
  paste0("iter",
         str_pad(string = c(1:nsims),width=nchar(nsims),side = "left",pad = "0"))
tic()
for(i in 1:nsims)
{
  indpsf_field_nsims[[i]] <- adatcalc(biomass_co = field_boot$t[i,c(1:17)],
                                      logodds_co = field_boot$t[i,c(18:34)])
  
   indpsf_shade_nsims[[i]] <- adatcalc(biomass_co = shade_boot$t[i,c(1:26)],
                                       logodds_co = shade_boot$t[i,c(27:52)])
  if(i %%100 == 0) {
       cat(paste0("currently on",i,"\n"))
       }
}
indpsf_field_nsims <- bind_rows(indpsf_field_nsims,.id = "iteration")
indpsf_shade_nsims <- bind_rows(indpsf_shade_nsims,.id = "iteration")
toc()

dat_indpsf_confint1 <- 
bind_rows(
  indpsf_field_nsims %>% 
  pivot_wider(id_cols = c("seed_source","soil_source"),
              names_from = iteration,
              values_from = alpha) %>% 
  mutate(tag = paste0(seed_source,"_",soil_source,"_field")) %>% 
  select(-seed_source,-soil_source) %>% column_to_rownames("tag"),
  
  indpsf_shade_nsims %>% 
  pivot_wider(id_cols = c("seed_source","soil_source"),
              names_from = iteration,
              values_from = alpha) %>% 
  mutate(tag = paste0(seed_source,"_",soil_source,"_shadehouse")) %>% 
  select(-seed_source,-soil_source) %>% column_to_rownames("tag"))

dat_indpsf_confint2 <-
  data.frame(
    lci = 
      apply(X = dat_indpsf_confint1,MARGIN = 1,
            FUN = function(x) quantile(x = x,prob = 0.025)),
    uci = 
      apply(X = dat_indpsf_confint1,MARGIN = 1,
            FUN = function(x) quantile(x = x,prob = 0.975))) %>%
  rownames_to_column("tag") %>%
  separate(col = tag,into = c("seed_source","soil_source","dataset"),sep = "_",remove = T)

dat_indpsf <- 
  full_join(x = bind_rows(indpsf_shade %>% mutate(dataset = "shadehouse"),
                          indpsf_field %>% mutate(dataset = "field")),
            y = dat_indpsf_confint2,
            by = c("seed_source","soil_source","dataset"))

dat_figa1 <- 
  dat_indpsf %>% 
  mutate(
    seed_myco = ifelse(seed_source %in% c("BC","HI"),"AM","EcM"),
    soil_myco = ifelse(soil_source %in% c("BC","HI"),"AM","EcM"),
    HA = ifelse(seed_source!=soil_source,"away","home"),
    combo = case_when(
           seed_myco == "AM" & soil_myco=="EcM" ~  "AM in EcM-trained soil",
           seed_myco == "AM" & soil_myco=="AM" ~  "AM in AM-trained soil",
           seed_myco == "EcM" & soil_myco=="AM" ~  "EcM in AM-trained soil",
           seed_myco == "EcM" & soil_myco=="EcM" ~  "EcM in EcM-trained soil"),
    soil_source = factor(soil_source,
                              levels = c("SC","ST","DZ","BC","HI")),
    seed_source = factor(seed_source,
                              levels = c("SC","ST","DZ","BC","HI")))

figa1_s <- 
  dat_figa1 %>% 
  filter(dataset == "shadehouse") %>% 
  ggplot(data = .,
       aes(y = alpha,x = soil_source,ymin = lci,ymax = uci)) + 
    geom_point(aes(colour = combo,
                   shape = HA),
               size = 4) + 
  geom_linerange() + 
  coord_flip() + 
  facet_wrap(.~seed_source,
             ncol = 1, scales = "free") + 
  theme_bw() + theme(legend.position = "top") + 
  scale_colour_manual(name="",values=c("#1065ab","#8ec4de","#f6a582","#b3152a")) + 
  scale_shape_manual(name="",values = c(16,1)) + 
  ylab("modelled AGB (g) \n shade house") + xlab("soil-source")  + guides(shape = F)

figa1_f <- 
  dat_figa1 %>% 
  filter(dataset == "field") %>% 
  ggplot(data = .,
       aes(y = alpha,x = soil_source,ymin = lci,ymax = uci)) + 
    geom_point(aes(colour = combo,
                   shape = HA),
               size = 4) + 
  geom_linerange() + 
  coord_flip() + 
  facet_wrap(.~seed_source,
             ncol = 1, scales = "free") + 
  theme_bw() + theme(legend.position = "top") + 
  scale_colour_manual(name="",values=c("#1065ab","#8ec4de","#f6a582","#b3152a")) + 
  scale_shape_manual(name="",values = c(16,1)) + 
  ylab("modelled AGB (g) \n field") + xlab("soil-source") + guides(shape = F)

figA1 <- 
  figa1_s + figa1_f + 
  plot_layout(guides = "collect",ncol = 2) & theme(legend.position = "top")

ggsave(filename = "results/figA1.png",
       plot = figA1,device = "png",width = 18,height = 18,units = "cm")
```

### Figure A2: phylogeny dist and Is values model
 
```{r}

isboth <- read_csv(file = "results/isboth.csv")
phyloboth <- 
  bind_rows(
  read_csv(file = "data/spsf_final.csv") %>% 
  select(Seedling.sp,Neighbour.sp,Phylodist) %>% distinct() %>%
  mutate(dataset = "shadehouse"),
  read_csv(file = "data/fpsf_final.csv") %>% 
  select(Seedling.sp,Neighbour.sp,Phylodist) %>% distinct() %>%
  mutate(dataset = "field"))

istot <- isboth %>%  
  separate(col = pair,into = c("sp1","sp2"),sep = "_",remove = T) %>% 
  left_join(y = phyloboth,
            by = c("sp1"="Seedling.sp","sp2"="Neighbour.sp","dataset"="dataset")) %>%
  rename(phylodist_Mya = Phylodist)

ms2 <- lm(data = istot, 
          formula = isval ~ phylodist_Mya)

figA2 <- jtools::effect_plot(model = ms2,pred = "phylodist_Mya",
                             interval = T,int.type = "prediction",plot.points = T) + 
  ylab("pairwise PSF - Is") + xlab("pairwise phylogenetic distance (Mya)")

ggsave(filename = "results/figA2.png",
       plot = figA2,
       device = "png",width = 10,height = 10,units = "cm",dpi = 300)
```
